Sampling requirements to detect ecosystem change

### 2020-03-05 R/manuscript_draft.Rmd
add package cowplot to the pacman loading package line. Correct typo on fig. 2

pacman::p_load(patchwork, stickylabeller, ggplot2, dplyr, wesanderson, reshape)
```

@@

p1 <- 
ggplot(simulation_all %>% filter(Parameter == unique(simulation_all$Parameter)[1]), aes(Param, min_time)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept=ar_vr$acf[2], lty=2) + 
  facet_wrap(~Parameter, scales="free_x", 
             labeller = label_glue('(a) {Parameter}')) +
  ylim(20,50) +
  labs(x=c("phi"), y= "Minimum number of samples required") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())

>>>>

pacman::p_load(patchwork, stickylabeller, ggplot2, dplyr, wesanderson, reshape, cowplot)
```

@@

p1 <- 
ggplot(simulation_all %>% filter(Parameter == unique(simulation_all$Parameter)[1]), aes(Param, min_time)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept=ar_vr$acf[2], lty=2) + 
  facet_wrap(~Parameter, scales="free_x", 
             labeller = label_glue('(a) {Parameter}')) +
  ylim(20,50) +
  labs(x=c("sigma"), y= "Minimum number of samples required") + 
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
